
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[]{deedy-resume-openfont}

\usepackage{xcolor}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\colorlet{BLUE}{RoyalBlue}

\namesection{\color{RoyalBlue}}{\color{RoyalBlue} Husni Almoubayyed}{ \urlstyle{same}\url{http://www.husni.space} \\
\href{mailto:husnial@cmu.edu}{husnial@cmu.edu} | (412) 345 $-$ 1875
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\color{Blue} Contact \& Links} 
Husni Almoubayyed,\\ 
Wean Hall 8419, \\ 5000 Forbes Ave, \\ Pittsburgh, PA 15213 \\
Phone: (412) 345 $-$ 1875 \\
Website: \href{https://www.husni.space}{\custombold{www.husni.space}} \\
Email: \href{mailto:husnial@cmu.edu}{\custombold{husnial@cmu.edu}} \\
Github: \href{https://github.com/hsnee}{\custombold{hsnee}} \\
LinkedIn:  \href{https://www.linkedin.com/in/husnialmoubayyed}{\custombold{husnialmoubayyed}} 
\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\color{Blue} Programming}
\location{Wrote reviewed \& shared libraries:}
\textbullet{} Python \textbullet{}  C/C++ \textbullet{} Unix/Shell  \\
\location{Experienced:}
\textbullet{} Matlab \textbullet{} Javascript \textbullet{} Mathematica  \\
\location{Familiar:}
\textbullet{} CSS \textbullet{} HTML \textbullet{} R \\
See Github (link above) for examples
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\color{Blue} Grants \& Awards} 
%$\;$
%\begin{tightemize}
\textbullet{} Royal Astronomical Society (RAS) Fellowship (2015 $-$ Present) \\
\textbullet{} Grants from Stanford/KIPAC (2017), \\ LSST Corporation (2017), CMU Provost's Office (2017), RAS (2015)\\
%\end{tightemize}
\sectionsep


\section{\color{Blue} Outreach}
\location{Pittsburgh Hack Hour} \textit{Organizer} (2017 $-$ Present (biweekly)) \\
\location{TheGIST Magazine} \textit{Specialist Editor} (2015 $-$ Present) \\
\location{Science Connects} \textit{STEM Ambassador for West of Scotland} (2015 $-$ 2016) \\
\location{Glasgow Science Festival} \textit{Offical Media Reporter} (2015) \\
\location{UKSEDS} \textit{Assistant Officer} (2015 $-$ 2016) \\
\location{WikiProject Physics} \textit{Contributor} (2015 $-$ Present) \\
\sectionsep


\section{\color{Blue} Affiliations} 

Royal Astronomical Society (Fellow)\\
LSST Dark Energy Science Collaboration (Member)\\
American Physical Society (Member) \\
Institute of Physics (Member) \\
LIGO Science Collaboration (Former Member) \\
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\section{\color{Blue} Education} 

\runsubsection{Carnegie Mellon University} \hfill \location{Fall 2016 $-$ Present}
\descript{PhD in Physics}
Pittsburgh, PA, USA
\sectionsep

\runsubsection{University of Glasgow} \hfill \location{Fall 2012 $-$ Spring 2016 }
\descript{BSc (Hons) in Astrophysics, with Honours of the First Class}
Glasgow, Scotland, UK. $\;\;$  \location{GPA: 4.0 / 4.0}
\sectionsep


\section{\color{Blue} Experience}

\runsubsection{Carnegie Mellon University} \hfill \location{Sep 2016 – Present}
\descript{Graduate Researcher | Large Synoptic Survey Telescope (LSST)}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}\item Writing Python libraries/metrics to measure impact of PSF modeling errors on weak lensing shear signal to give feedback on LSST algorithms. \item Worked on numerically validated Core Cosmo Library (Python \& C$++$)
\end{tightemize}
\descript{Graduate Teaching Assistant }
% \vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}\item Led recitations, wrote programming labs/exercises, held office hours.
\item Participated in CMU's Eberly Teaching Excellence center, rated consistently $>$1 standard deviation above dept average.
\end{tightemize}
\sectionsep

\runsubsection{University of Glasgow} \hfill \location{Sep 2015 – May 2016}
\descript{Undergraduate Researcher | Laser Interferometer Gravitational Wave Observatory (LIGO)}
\begin{tightemize}
\item Worked on time-series data analysis of LIGO's data ($\sim$1.5 yrs of data).\item Used Bayesian inference to set upper limits on GW signal from the Sun. \item Presented work as a talk (U. Glasgow) and poster (U. Southampton). \item Contributed to LIGO signal searches (co-authored 2 journal papers). \end{tightemize}
\descript{Undergraduate Teaching Assistant}
\sectionsep

\runsubsection{Durham University} \hfill  \location{May 2015 – Aug 2015}
\descript{Undergraduate Researcher | Dark Energy Spectroscopic Instrument (DESI)}

\begin{tightemize}
\item Wrote parallelized modules in C \& Python to mitigate bias in galaxy clustering due to redshift incompleteness caused by fiber collisions. \item Published results as talk in CosPA Symposium (KAIST, Daejeon, S. Korea) \end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\color{Blue} Workshops}
\descript{Citadel LLC/Correlation One Datathon}
\location{Sep 2017 | CMU, Pittsburgh, PA}
In under 7 hours, I used large datasets to create a Bayesian model to predict posterior probability of cancer from DNA expression level.
\sectionsep

\descript{LSST Corporation Hack Week}
\location{Jul 2017 | Fermi National Lab, Batavia, IL}
Wrote Core Cosmology Library code, particularly MCMC likelihood analyses.
\sectionsep


\descript{Next Gen Computational Modelling Summer Academy}
\location{Jun 2016 $+$ Jun 2015 | U. Southampton, Southampton, UK}
Presented research poster. Worked on pandas \& scikit-learn packages, CUDA parallel programming, and FEM Modelling
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SOCIETIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\end{minipage} 
\end{document}