
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[]{deedy-resume-openfont}

\usepackage{xcolor}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\colorlet{BLUE}{RoyalBlue}

\namesection{\color{RoyalBlue}}{\color{RoyalBlue} Husni Almoubayyed}{ \urlstyle{same}\url{http://www.husni.space} |
\href{mailto:husnial@cmu.edu}{husnial@cmu.edu} | (412) 345 $-$ 1875
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
$\; 
\;
\;$


\section{\color{Blue} Contact \& Links} 
Husni Almoubayyed,\\ 
Wean Hall 8419, \\ 5000 Forbes Ave, \\ Pittsburgh, PA 15213 \\
Github: \href{https://github.com/hsnee}{\custombold{hsnee}} \\
LinkedIn:  \href{https://www.linkedin.com/in/husnialmoubayyed}{\custombold{husnialmoubayyed}} 
\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\color{Blue} Programming}
\location{Wrote and published reviewed libraries in:}
\textbullet{} Python  \textbullet{} Unix/Shell \textbullet{} Matlab \textbullet{} \LaTeX   \\
 \textbullet{} Javascript \textbullet{} Mathematica  \textbullet{}  C/C++\\
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\color{Blue} Grants \& Awards} 
%$\;$
%\begin{tightemize}
\textbullet{} Royal Astronomical Society (RAS) Fellowship (2015 $-$ Present) \\
\textbullet{} Grants from Stanford/KIPAC (2017, 2018), LSST Corporation (2017), CMU Provost's Office (2017) \\ Royal Astron Society (2015, 2017)\\
%\end{tightemize}
\sectionsep


\section{\color{Blue} Outreach}
\location{Pittsburgh Hack Hour} \textit{Organizer} (2017 $-$ Present (biweekly)) \\
\location{TheGIST Magazine} \textit{Specialist Editor} (2015 $-$ Present) \\
\location{Science Connects} \textit{STEM Ambassador for West of Scotland} (2015 $-$ 2016) \\
\location{Glasgow Science Festival} \textit{Offical Media Reporter} (2015) \\
\location{UKSEDS} \textit{Assistant Officer} (2015 $-$ 2016) \\
\location{WikiProject Physics} \textit{Contributor} (2015 $-$ Present) \\
\sectionsep


%\section{\color{Blue} Affiliations} 

%Royal Astronomical Society (Fellow)\\
%LSST Dark Energy Science Collaboration (Member)\\
%American Physical Society (Member) \\
%Institute of Physics (Member) \\
%LIGO Science Collaboration (Former Member) \\
%\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vfill\vfill
$\;$
\vfill

%\Large{Interested in Data Science opportunities for Summer '18.}

\section{\color{Blue} Education} 

\runsubsection{Carnegie Mellon University} \hfill \location{Fall 2016 $-$ Present}
\descript{PhD in Physics \hfill Pittsburgh, PA, USA.}

\sectionsep

\runsubsection{University of Glasgow} \hfill \location{Fall 2012 $-$ Spring 2016 }
\descript{BSc (Hons) in Physics and Astrophysics, with Honours of the First Class. \hfill Glasgow, Scotland, UK.}% \location{GPA: 4.0 / 4.0}}
\sectionsep


\section{\color{Blue} Experience}

\runsubsection{Carnegie Mellon University} \hfill \location{Sep 2016 – Present}

\descript{Graduate Researcher | Large Synoptic Survey Telescope (LSST)}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize} \item Writing Python libraries/metrics to create an optimal 10-year strategy for the LSST (largest galaxy survey in history -- 10s of billions of galaxies), and leading Weak Lensing working group survey strategy efforts. \item Worked on numerically validated Core Cosmo Library (Python \& C++).
\end{tightemize}
\sectionsep

\descript{Graduate Teaching Assistant (2016$-$2017)}
\begin{tightemize} \item Won Best TA Award for 2016$-$2017 academic year
\end{tightemize} 
\sectionsep

\sectionsep

% \vspace{\topsep} % Hacky fix for awkward extra vertical space
%\begin{tightemize}\item Led recitations, wrote programming labs (Python), held office hours.
%\item Rated consistently $>$1 standard deviation above dept average.
%\end{tightemize}
%\sectionsep

\runsubsection{University of Glasgow} \hfill \location{Sep 2015 – May 2016}

\descript{Undergraduate Researcher | Laser Interferometer Gravitational Wave Observatory (LIGO)}
\begin{tightemize}
\item Worked on 2017 Nobel Prize-winning project, co-authored 2 journal papers, presented a talk (U. Glasgow) and a poster (U. Southampton).\item Used Bayesian inference to set upper limits on gravitational wave signal from the Sun using time-series datasets ($\sim$1.5 yrs of data). \end{tightemize}
\sectionsep

\descript{Undergraduate Teaching Assistant}
\sectionsep
\sectionsep

\runsubsection{Durham University} \hfill  \location{May 2015 – Aug 2015}

\descript{Undergraduate Researcher | Dark Energy Spectroscopic Instrument (DESI)}

\begin{tightemize}
\item Wrote parallelized modules in C \& Python to mitigate bias in galaxy clustering due to redshift incompleteness caused by fiber collisions. \item Published results (talk) at CosPA '15 Symp. (KAIST, Daejeon, S. Korea) \end{tightemize}
\sectionsep
\end{minipage} 
%\begin{minipage}[t]{1\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\color{Blue} Workshops \& Competitions}
\begin{minipage}{0.5\textwidth} 


\descript{Pittsburgh Innovation Case Competition $-$ Grand Prize Winner}
\location{Oct 2019 | Pittsburgh, PA}
Evaluated the profitability of Google's cloud gaming product; endorsed immediate market entry, and made 3 recommendations over short and long terms that maximize profit, user base, and market share.
\sectionsep


\descript{Oath/Verizon Discovery ChatBot Hackathon $-$ Grand Prize Winner}
\location{Oct 2017 | CMU, Pittsburgh, PA}
Created a chatbot incorporating Natural Language Processing and neural networks to make movie recommendations.
\sectionsep

\descript{Hack-A-Startup 2017 $-$ Runner-up}
\location{Oct 2017 | Tepper School of Business, CMU}
Worked on Optipik, a CMU startup that uses Deep\\ Learning (CNNs) for photo optimzation.
\sectionsep




\end{minipage}%
\begin{minipage}{0.5\textwidth}

\descript{Red Bull Hack The Hits $-$ Finalist Award}
\location{Nov 2017 | San Francisco, CA}
Built a music-making (in Python) graphical tablet with visual representation (in Processing.JS).
\sectionsep

\descript{Citadel LLC/Correlation One Datathon}
\location{Sep 2017 | CMU, Pittsburgh, PA}
In <7 hours, I used big datasets to create a Bayesian model to predict posterior probability of cancer from DNA expression.
\sectionsep

%\sectionsep
%\descript{Next Gen Comp Modeling Summer Academy}
%\location{Jun 2016 $+$ Jun 2015 | U. Southampton, Southampton, UK}
%Worked on pandas \& scikit-learn (Python); CUDA (GPUPP in C)
%\sectionsep

\end{minipage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SOCIETIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%\end{minipage} 
\end{document}
